### 2023-07-11 tesis_Ashish/Chapter4/chapter4.tex
thesis version 11 Jul

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
\caption{%                                                                                                                                                                                                      
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_L0_veto}
\end{figure}

@@

\begin{table}[!ht]
\centering
\topcaption{%
    PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
}
\begin{tabular}{ccccc}
    \textbf{Period} & \textbf{mean} & \textbf{rms} &  \textbf{rms/mean} \\ \hline
    A & 1.006 & 0.004183 & 0.004158 \\
    B & 0.9981  & 0.003133 & 0.0031389 \\
    C & 0.9989  & 0.003009 & 0.003012\\
    D1 & 1.003  & 0.002441 & 0.002433 \\
    D2 & 1.001  & 0.0029 & 0.00289 \\
   D3  & 1  & 0.002115 & 0.002115 \\
   D4  & 1.002  & 0.003673 & 0.003666 \\ 
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
\caption{%
   klm
}
\label{fig:old_new_vetolist}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
\caption{%
pcc layer disk mean rms
}
\label{fig:pixellalyerdiskmeanrms}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type2_af_parameters.png}
\caption[]{%                                                                                
  Afterglow fit model.
}
\label{fig:af_fit}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/stability_sys.png}
\caption[]{%                                                                                                                                                                                                                 
  Stability systematic uncertainty.
}
\label{fig:af_fit}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/linearity_sys.png}
\caption[]{%                                                                                                                                                                                                                \

  Linearity systematic uncertainty.
}
\label{fig:af_fit}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1_res.png}
\caption[]{%                                                                                                                                                                                                      
   Type 1 residual.                                                                                                                                                                                                              
}
\label{fig:type1}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
\caption[]{%

  Type 2 residuals.
}
\label{fig:type2}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
\caption[]{%                                                                                                                                                                                                              
   Type 1 residual fraction.                                                                                                                                                                                                      
}
\label{fig:type2}
\end{figure}

@@

>>>>

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
%\caption{%                                                                                                                                                                                          
 %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
%}
%\label{fig:PCC_stab_begin}
%\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
%\caption{%                                                                                                                                                                                                            
 %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
%}
%\label{fig:PCC_stab_begin}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto.png}
\caption{%                                                                                                                                                                
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
%\caption{%                                                                                                                                                                           
 %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
%}
%\label{fig:PCC_stab_L0_veto}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_B0_veto.png}
\caption{%                                                                                                                                                                           
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_L0_veto}
\end{figure}

@@

\begin{table}[!ht]
\centering
%\topcaption{%
 %PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
%}
\begin{tabular}{ccccc}
    \textbf{Period} & \textbf{mean} & \textbf{rms} &  \textbf{rms/mean} \\ \hline
    A & 1.006 & 0.004183 & 0.004158 \\
    B & 0.9981  & 0.003133 & 0.0031389 \\
    C & 0.9989  & 0.003009 & 0.003012\\
    D1 & 1.003  & 0.002441 & 0.002433 \\
    D2 & 1.001  & 0.0029 & 0.00289 \\
   D3  & 1  & 0.002115 & 0.002115 \\
   D4  & 1.002  & 0.003673 & 0.003666 \\ 
\end{tabular}
\caption{%                                                                                                                                                                                              
 PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
}
\label{tab:pccvis_diffveto}
\end{table}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
%\caption{%
 %  klm
%}
%\label{fig:old_new_vetolist}
%\end{figure}

\begin{table}[htbp]
\centering
\label{tab:run-period}
\begin{tabular}{cccc}
\textbf{Run period (Old Veto)} & \textbf{Good modules} & \textbf{Run period (New Veto)} & \textbf{Good modules} \\
\hline
A & 787 & A & 580 \\
B & 787 & B & 1054 \\
C & 787 & C & 780 \\
D early & 787 & D1 & 687 \\
 & & D2 & 672 \\
 & 775 & D3 (323363-323699)  & \\
D late & 469 & D3 (323700-324420) & 775 \\
 & 824 & D4 & \\
\end{tabular}
\caption{Run Period and Good Modules}
\end{table}

@@

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
%\caption{%
%pcc layer disk mean rms
%}
%\label{fig:pixellalyerdiskmeanrms}
%\end{figure}

\begin{table}[htbp]
\centering
%\caption{Layer/Disk Statistics}
\label{tab:layer-disk}
\begin{tabular}{cccccc}
\textbf{Layer/Disk} & \textbf{Good modules} & \textbf{mean} & \textbf{rms} & \textbf{rms/mean} \\
\hline
Layer 2 & 0 & 0 & 0 & 0 \\
Layer 3 & 48 & 0.374681 & 0.000663165 & 0.00176995 \\
Layer 4 & 79 & 0.356424 & 0.000724235 & 0.00203195 \\
Disk 1 & 10 & 0.102687 & 0.000535149 & 0.00521144 \\
Disk 2 & 12 & 0.112508 & 0.000460595 & 0.00409389 \\
Disk 3 & 6 & 0.0537002 & 0.000282446 & 0.00525967 \\
Total  & 155 & & \\
%\multicolumn{2}{c}{} & \multicolumn{2}{r}{155} \\
\end{tabular}
\caption{Layer/Disk Statistics}
\end{table}

@@

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/type2_af_parameters.png}
%\caption[]{%                                                                                
 % Afterglow fit model.
%}
%\label{fig:af_fit}
%\end{figure}

\begin{table}
  \centering
  \begin{tabular}{ccc}
    \textbf{\# of wagon} & \textbf{a} & \textbf{b} \\
     \hline
   1-wagon train  & 0.001246  & 0.01261 \\
   2-wagon train  & 0.000813 &  0.01219\\
   3-wagon train  & 0.0008265 &  0.01231\\
  \end{tabular}
  \caption{type 2  af parameters}
\end{table}

@@

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/stability_sys.png}
%\caption[]{%                                                                                                                                                                                                                 
 % Stability systematic uncertainty.
%}
%\label{fig:af_fit}
%\end{figure}

@@

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/linearity_sys.png}
%\caption[]{%                                                                                                                                                                                               %                 \

 % Linearity systematic uncertainty.
%}
%\label{fig:af_fit}
%\end{figure}

@@

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/type1_res.png}
%\caption[]{%                                                                                                                                                                                                      
 %  Type 1 residual.                                                                                                                                                                                                              
%}
%\label{fig:type1}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5.png}
\caption[]{%                                                                                                                                                                                              
   Type 1 residual.

}
\label{fig:type1}
\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
%\caption[]{%

 % Type 2 residuals.
%}
%\label{fig:type2}
%\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5.png}
%\caption[]{%

 % Type 2 residuals.
%}
%\label{fig:type2}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5_rangefixed.png}
\caption[]{%                                                                                                                                                                                              
  Type 2 residuals.  Mean value is 0.00267652.
 }
\label{fig:type2}
\end{figure}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
%\caption[]{%                                                                                                                                                                                                              
 %  Type 1 residual fraction.                                                                                                                                                                                                      
%}
%\label{fig:type2}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1frac_gr0p5.png}
\caption[]{%                                                                                                                                                                                              
   Type 1 residual fraction.                                                                                                                                                                              
}
\label{fig:type2}
\end{figure}

@@

\begin{table}[htbp]
\centering
\caption{Systematic Uncertainty}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
\textbf{N/I} & \textbf{Systematic names} & \textbf{Uncertainty (PAS) [\%]} & \textbf{Uncertainty (Final veto) [\%]} \\
\hline
Normalization & length scale & &  \\
 & Orbit drift &  &  \\
 & X-Y nonfactorization & 2 & 0.4 \\
 & Beam-beam deflection & -- & -- \\
 & Dynamic beta & -- & -- \\
 & Beam current calibration & -- & -- \\
 & Ghost and satellite & -- & -- \\
 & Scan to scan variation & 0.3 & 0.3 \\
 & Bunch to bunch variation & 0.3 & 0.1 \\
 & Cross detector consistency & -- & -- \\
 & Background subtraction & 0.1 & 0.06 \\
Integration & Afterglow & 0.5 & 0.3 \\
 & Cross detector stability & 0.6 & 0.24 \\
 & Linearity & 1.1 & 0.35 \\
Total & -- & 2.47 & 0.813 \\
\end{tabular}
\end{table}
